### 2015-02-02 paper/intro.tex
results
revised intro

\section{Introduction}
In this work, we study the noise sensitivity of the state-of-the-art for route flow estimation for mobility cyber-physical systems (CPS). Route flow estimation on road networks is a critical problem for mobility CPS, as any prediction and control applications require accurate and reliable estimates of the state of the road network. Previous work has demonstrated the promise of using cellular towers as sensor inputs to a convex optimization formulation of the problem, along with a projected first-order method that scales well to large city-scale networks \cite{Wu2015}. However, the work uses entirely synthetic data which assumes that vehicles are connected to the closest cell tower throughout their trajectories (i.e. voronoi partitions). In

>>>>

\section{Introduction}
Route flow estimation on road networks is a critical problem for mobility CPS, as real-time prediction and control applications require the state of the road network. Previous work has demonstrated the promise of computing an estimate from area-based sensors such as cellular towers, using a projected first-order method that scales well to large city-scale networks \cite{Wu2015}. Importantly, the work's introduction of \textit{cellpaths} -- cell tower connection sequences -- helps to cope with the underdetermined-ness of the problem. However, previous analysis has been based off of noiseless synthesized data, which makes the strong but common assumption that vehicles are connected to the closest cell tower throughout their trajectory (i.e. voronoi tessellations of cell tower regions) \cite{Voronoi1908}. The real world is seldom so kind.

In this work we analyze the sensitivity of the flow estimation procedure to structured noise. In particular, we consider the effect of a handoff model for within the cellular network, which includes hysteresis margins for handoffs and cell tower load balancing, in the presence of RF interference.

### 2015-02-02 paper/model.tex
revised intro

\subsection{System model}
This work models the assignment of individual vehicles to cell towers with an effective received signal strength (eRSS) based decision process.  This eRSS between a vehicle $v$ and a cell tower $t$ is calculated from the received power by introducing tower handoff dynamics as noise penalties;
each vehicle gets assigned to the cell tower with the highest eRSS value at each time point in the simulation.
All towers are assumed to output with the same transmit power, so eRSS can be calculated in dB as: \begin{eqnarray}
  eRSS_{v-t} & = & \left( \frac{P_{RX_v}}{P_{TX_t}} \right)_{dB} 
                   + P_{handoff_{v-t}} \\
  & = & P_{d_{v-t}} +P_{int} + P_{hyst_{v-t}} + P_{load_t}.
\end{eqnarray}

In this equation, the actual received signal strength is composed of two parts, $P_d$ and $P_{int}$.  The attenuation due to path loss is given by: \begin{equation}
  P_{d_{v-t}} = -10 \gamma \log_{10} d_{v-t},
\end{equation}
where $d_{v-t}$ is the distance between the vehicle and the cell tower, and $\gamma$ is the path loss exponent.  The additional attenuation due to interference, multipath effects, and other RF noise is wrapped up into a uniformly distributed random penalty: \begin{equation}
  P_{int} = -\alpha \cdot \mathrm{Unif}(0,1).
\end{equation}

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers: \begin{equation}
  P_{hyst_{v-t}} = \begin{dcases}
    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
    0 & \mathrm{otherwise.}
  \end{dcases}
\end{equation}
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers: \begin{equation}
  P_{load_t} = -\xi \cdot N_{t},
\end{equation}
where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.

>>>>

\section{Problem formulation}
\label{sec:system-model}

\subsection{Route flow estimation}
The route flow estimation problem (illustrated in Fig.~\ref{fig:example-setup}) is as follows: for a road network $G=(V,E)$, let $\mathcal{R}$ denote the set of $n$ routes that vehicles take.  The route flow $x \in \mathbb{R}^n$ is the unknown state of the road network.  We employ sensor measurments cellpath flow $f$, origin-destination (OD) flow $d$, and link flow $b$.  We are given the linear operators $U, T, A$ relating the sensor measurements to the route flow $x$, that is, $Ax=b, Tx=d, Ux=f$. We wish to estimate the state $x$ from the sensor data $f,d,b$.

With the exception of the noise model, we follow the same assumptions as in \cite{Wu2015}: static setting, and continuous and well-posed cellpaths.

\begin{figure}[htb]
  \centering
    \includegraphics[width=0.47	\textwidth]{figures/setup}
  \caption{\footnotesize{In this illustration, we have two origins A and C ({\color{blue}blue}) and one destination B ({\color{red}red}). We have routes $r_1,r_2,r_3,r_4$ with flows $x=(x_1,x_2,x_3, x_4)$ such that $r_1,r_2$ go from A to B and $r_3,r_4$ go from C to B. Cells $c_1,\cdots,c_7$ are shown in {\color{magenta} purple} dashed regions. Since route $r_1$ goes through cells $c_1,c_2,c_3,c_4$, its associated cellpath is $p_{1234}$. Similarly, routes $r_2,r_3,r_4$ have cellpaths $p_{1654},p_{654},p_{654}$ respectively. Let $f_{p1234},\,f_{p1654},\,f_{p654}$ be the cellpath flows (obtained from cellular network data), \emph{i.e.} there are $f_{p1234}$=1000~veh/h going through $c_1,c_2,c_3,c_4$. Let $d_{AB}$ and $d_{CB}$ be the OD demands and $b$ be the link flow ({\color{green}green}, from loop detectors). Without considering data from cellpaths, the problem has \emph{one degree of freedom} and is \emph{underdetermined} with only the OD demands as data.}}
  \label{fig:example-setup}
\end{figure}

\subsection{Cell tower handoff noise model}

This work models the assignment of individual vehicles to cell towers with an effective received signal strength (eRSS) based decision process.  This eRSS between a vehicle $v$ and a cell tower $t$ is calculated from the received power by introducing tower handoff dynamics as noise penalties;
each vehicle gets assigned to the cell tower with the highest eRSS value at each time point in the simulation.

\begin{eqnarray}
  eRSS_{v-t} & = & \left( \frac{P_{RX_v}}{P_{TX_t}} \right)_{dB} 
                   + P_{handoff_{v-t}} \\
  & = & P_{d_{v-t}} +P_{int} + P_{hyst_{v-t}} + P_{load_t}, \\
  P_{d_{v-t}} & = & -10 \gamma \log_{10} d_{v-t}, \\
  P_{int} & = & -\alpha \cdot \mathrm{Unif}(0,1). \\
  P_{hyst_{v-t}} & = & \begin{dcases}
    \beta & \mathrm{if~} v \mathrm{~is~already~connected~to~} t, \\
    0 & \mathrm{otherwise,}
  \end{dcases} \\
  P_{load_t} & = & -\xi \cdot N_{t}.
\end{eqnarray}

In this equation, the actual received signal strength is attenuated by two sources: the path loss $P_d$ 
is a function of the distance between the vehicle and the cell tower $d_{v-t}$ and path loss exponent $\gamma$, while 
interference, multipath effects, and other RF noise are wrapped up into a uniformly distributed random penalty $P_{int}$.

The dynamics of the tower handoff, $P_{handoff}$, are modelled using two parameters.  $P_{hyst}$ represents an amount of hysteresis in the system by boosting the eRSS of the currently associated tower, biasing individual vehicles against switching towers.
$P_{load}$ represents the load balancing efforts to distribute usage across the cell network, adding an eRSS penalty to heavily loaded towers.

where $N_t$ is the number of other vehicles already connected to tower $t$.  The four parameters $\{\gamma, \alpha, \beta, \xi\}$ can be scaled by the first to get our final parameter vector $\phi = \{a, b, c\} = \{\alpha/\gamma, \beta/\gamma, \xi/\gamma\}$ over which we conduct our sensitivity analysis, evaluating the relative impacts of hysteresis and load balancing in the presence of RF noise on route flow estimation.
